|

### 2022-02-19 paper/dcpo_demsupport.Rmd
clean up

Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion, latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @BoundEtAl2001, 3709; @CaugheyWarshaw2018a, 254].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @SolisWaggoner2021, 18; @GandhiSumner2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @KastellecEtAl2015, 791-792; @CaugheyWarshaw2018a, 254]. 
Therefore, after replicating the original analyses that use only the point estimates for public support and the other variables included in the model, we perform the analyses again only this time incorporating uncertainty in the articles' models using our replicated data.
We conduct inferences from the distributive data via the technique known as the "method of composition"  [MOC, @Tanner1993, 52].
MOC accounts for uncertainty from opinion estimates and analysis models through each modeling stage.
In the analysis stage, uncertainty is incorporated through simulation based on the variance-covariance matrix of a model without requiring any change to its specification.
This allows MOC to be broadly applicable adapt to many different types of models, including time-series-cross-sectional models [@CaugheyWarshaw2018a, A15-16], Cox proportional hazards models [@TreierJackman2008, 215], or models of individual-level roll call voting [@KastellecEtAl2015, 791].^[For additional details on the MOC technique, see  OSM \@ref(moc).]

>>>>

Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion, latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @BoundEtAl2001, 3709; @CaugheyWarshaw2018a, 254].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @SolisWaggoner2021, 18; @GandhiSumner2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @KastellecEtAl2015, 791-792; @CaugheyWarshaw2018a, 254]. 
Therefore, after replicating the original analyses that use only the point estimates for public support and the other variables included in the model, we perform the analyses again only this time incorporating uncertainty in the articles' models using our replicated data.
We conduct inferences from the distributive data via the technique known as the "method of composition"  [MOC, @Tanner1993, 52].
MOC accounts for uncertainty from opinion estimates and analysis models through each modeling stage.
In the analysis stage, uncertainty is incorporated through simulation based on the variance-covariance matrix of a model without requiring any change to its specification.
This allows MOC to be broadly applicable to many different types of models, including time-series-cross-sectional models [@CaugheyWarshaw2018a, A15-16], Cox proportional hazards models [@TreierJackman2008, 215], or models of individual-level roll call voting [@KastellecEtAl2015, 791].^[For additional details on the MOC technique, see  OSM \@ref(moc).]
